---
title: "Hakalar2000_HomeworkOriginal"
author: "Me"
date: "September 16, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This is code for [Homework 2](https://fuzzyatelin.github.io/bioanth-stats/homework-02.html), on week threee of AN597 associated with module 6 and 7. 

>Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

* problem 1
* problem 2
* problem 3
* problem 4
* problem 5
* problem 6

Mean = 15
Poisson Random Variable = X
Time Frame: 2 hours

What is Poisson Distribution?
* The experiment results in outcomes that can be classified as successes or failures. Calls or no calls, and how many calls. 
* The average number of successes (μ) that occurs in a specified region is known. We believe the average is 15 calls in a 2 hour period.
* The probability that a success will occur is proportional to the size of the region. A region includes a time frame, in this case two hours. 
* The probability that a success will occur in an extremely small region is virtually zero. No calls in like 5 minutes but many calls in 2 hours.

A poison random variable is the number of successes that result from a Poisson experiment.

Question 1: What is the probability that she will hear more than 8 calls during any given session?
```{r}
#We will use the function ppois since it calculates the poisson probability for a variable that is not discrete. A discrete variable would be like exactly 8 calls, but we want to know the probablity of 8 calls and more.
#lambda is equal to the mean so lambda<-15
#q is equal to the number of success, in this case 8+
#lower.tail is equal to TRUE if you want the probability of more than a certain number and FALSE if you want probability of less than a certain number. Because we want to know the probability of the 8+ we want to use TRUE. The default for this function is TRUE so we don't actually have to using lower.tail = TRUE in our function. 

#ppois(q, lambda, lower.tail)
Probability<-ppois(q = 8, lambda = 15)
Probability
```

Question 2: What is the probability that she will hear no calls in a session?
```{r}
#Now we have a discrete value of 0 which means we want to use dpois.
#same variables as above except q = 0. 
Probability<-dpois(0, lambda = 15)
Probability
#As you can see, there is very very low probability of our scinetist hearing nothing. 
```

Question 3: What is the probability that she will hear exactly 3 calls in a session?
```{r}
#same as above but we replace 0 with 3
Probability<-dpois(3, lambda = 15)
Probability
#Still low but more likely than 0 calls. 
```

Question 4: Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
```{r}

```

Question 5: Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).
```{r}

```

Question 6: Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?
```{r}

```



If it dissapears, make a change and save it. 


Make a list (numbers)
<ol>
<li>problem 1</li>
<li>problem 2</li>



